---
title: "manhattan"
---

## Single GWAS
```{r}
library(topr)
```


```{r, fig.width=10, fig.height=4}
manhattan(CD_UKBB)
```

Annotate the top association peaks with the nearest gene

```{r, fig.width=10, fig.height=4}
manhattan(CD_UKBB, annotate=5e-09)
```

Extract the lead snps and display them in red on the manhattan plot

```{r, fig.width=10, fig.height=4.5, warning=F, message=F}
lead_snps <- get_lead_snps(CD_UKBB, thresh = 5e-09, region_size = 10000000)
```

```{r, fig.width=9, fig.height=4, warning=F, message=F}
manhattan(list(CD_UKBB, lead_snps), 
          annotate=c(5e-100, 5e-09), 
          color=c("darkblue","red"), 
          legend_labels=c("CD UKBB", "Lead snp's"), verbose=F) 
```

Change the annotation to vertical and italic. Reduce the size of all text by setting the <code>scale</code> argument to 0.9. Move the legend labels to the top.

<details>

<summary><i>Click here to see the command </i></summary>

```{r, fig.width=9, fig.height=4, warning=F, message=F}

manhattan(list(CD_UKBB, lead_snps), 
          annotate=c(5e-100, 5e-09), 
          color=c("darkblue","red"), 
          legend_labels=c("CD UKBB", "Lead snp's"), 
          size=c(1,1.7),
          shape=c(19,8), 
          label_size = 3.7, 
          angle = 90, 
          label_fontface = "italic", 
          nudge_y = 5, 
          scale=0.9, 
          legend_position = "top", 
          ymax=32,  
          even_no_chr_lightness = c(0.8,0.5),
          verbose=F) 
```

</details>

<details>

<summary><i>Click here to see the command </i></summary>

```{r, echo=F}

top_snps_finngen <- get_lead_snps(CD_FINNGEN)
mh <- manhattan(list(CD_UKBB, lead_snps, top_snps_finngen),  color=c("red","darkred","gray40"),label_fontface = c("italic","bold","plain"), angle=c(90,0,0),
          legend_labels = c("CD","top snps UKB", "top snps Finngen"),annotate=1e-20, build=enshuman::hg38)
```

</details>

```{r, fig.width=9, fig.height=4, warning=F, message=F}
mh
```

<summary><i>Click here to see the command </i></summary>

```{r, eval=F}

top_snps_finngen <- get_lead_snps(CD_FINNGEN)
mh <- manhattan(list(CD_UKBB, lead_snps, top_snps_finngen),  color=c("red","darkred","gray40"),label_fontface = c("italic","bold","plain"), angle=c(90,0,0),
          legend_labels = c("CD","top snps UKB", "top snps Finngen"),annotate=1e-20, build=enshuman::hg38)
```

</details>

## Multi GWAS
